Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-05 tex/older_tex/VHzQ_20190531.tex

This paper is organized as follows.  In Section 2, we present the assembled list of the 463 $z\geq5.00$ VH$z$Qs that we have compiled. We then give a high-level overview of the photometric surveys and datasets we use and present the photometry of the VH$z$Qs. In Section 3 we ... and In Section 4 we ... We conclude in Section 5 and present all the necessary details to obtain our dataset in the Appendices.

We present all our photometry and magnitudes on the AB zero-point system \citep{Oke_Gunn1983, Fukugita1996}.  This includes the near-infrared, as well as the mid-infrared magnitudes. Appendix~\ref{sec:filters} gives the AB to Vega transforms for a wide range of optical, NIR and MIR filters. We use a flat $\Lambda$CDM cosmology with $H0 = 67.7$ km s$-1$ Mpc$−1$, $\Omega_{\rm M} = 0.307$, and $\Omega_{\Lambda} = 0.693$ (Planck Collaboration et al. 2016) to be consistent with \citet{Banados2016} and all logarithms are to the base 10.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%    S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%    S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%    S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
%%trim=l b r t
%  \includegraphics[width=18.6cm, clip,trim=14mm 4mm 10mm 10mm]
  \includegraphics[width=8.6cm, clip,trim=32mm 4mm 32mm 10mm]
  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/filters_vs_QSOstars_z7pnt0.pdf}
  \centering
  \vspace{-12pt}
  \caption[]
  {The spectral bands used by different survey telescopes and that are relevant here.
    The $grizy$ filters are from the Pan-STARRS survey. The $JHK$ are from 
    UKIRT/WFCAM, while $K_{s}$ is a VISTA/VIRCAM filter. The 
    The narrow W-band centered at $\lambda\approx14,500$\AA\ is a CFHT/Wircam filter. 
    [NJC: Do we use the W-band anywhere?]
    The WISE passbands  W1-4 are also presented.
    The quasar spectrum is a composite based on \citet{VdB2001} and 
    \citet{Banados2016}. The L and T dwarf spectra are from \citet{Cushing2006}. 
  }
  \label{fig:filters}
\end{figure}

@@

We have compiled a list of 463 quasars with redshifts $z\geq5.00$. We use all the $z\geq5.00$ quasars that have been discovered, spectroscopically confirmed and published as of 2018 December 31 (MJD 58483). We then obtain optical, near-infrared and mid-infrared photometry for the spectral dataset. The optical data comes from the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) survey \citep{Chambers2016}. The near-infrared data comes from two sources: first, the WFCAM \citep[][]{Casali2007} on the UKIRT, primarly, but not exclusively, as part of the UKIRT Infrared Deep Sky Survey \citep[UKIDSS; ][]{Lawrence2007}.  And second, data from the VIRCAM on the VISTA \citep[][]{Emerson2006, Dalton2006}. The mid-infrared, $\lambda=3-30\mu$m wavelength data is from the the Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010, Cutri2013} mission. For reference, Figure~\ref{fig:filters} displays the wavelength and normalised transmission of the filters in question.

\subsection{Spectroscopy} 
We compile the list of all known, spectroscopically confirmed
quasars from the literature.  This list was complied from a range of
surveys and papers.  Specifically, we use data from:
\citet{Banados2014, Banados2016, Banados2018}, 
\citet{Becker2015}, 
\citet{Calura2014}, 
\citet{Carilli2007, Carilli2010}, 
\citet{Carnall2015}, 
\citet{Cool2006}, 
\citet{DeRosa2011}, 
\citet{Fan2000, Fan2001c, Fan2003, Fan2004, Fan2006, Fan2018}, 
\citet{Goto2006}, 
\citet{Ikeda2017}, 
\citet{Jiang2008, Jiang2009, Jiang2015, Jiang2016},   
\citet{Kashikawa2015}, 
\citet{Koptelova2017}, 
\citet{Kim2015, Kim2018},  
\citet{Kurk2007, Kurk2009}, 
\citet{Leipski2014}, 
\citet{Mahabal2005}, 
\citet{Matsuoka2016,  Matsuoka2018a, Matsuoka2018b},   
\citet{Mazzucchelli2017}, 
\citet{Morganson2012}, 
\citet{Mortlock2009, Mortlock2011},
\citet{McGreer2006, McGreer2013},  
\citet{Reed2015, Reed2017}, 
\citet{Stern2007},  
\citet{Tang2017}, 
\citet{Venemans2007, Venemans2012, Venemans2013, Venemans2015a, Venemans2015b, Venemans2016},
\citet{WangF2016, WangF2017, WangF2018a, WangF2018b},
\citet{Willott2007, Willott2009, Willott2010a, Willott2013b, Willott2015}, 
\citet{Wu2015} 
\citet{YangJ2018a, YangJ2018b}  
and 
\citet{Zeimann2011}. 
%We have obtained a list of 463 spectroscopically confirmed quasars with redshifts $z\geq5.00$.

@@

  We detect 359 unique quasars in the WFCAM WSA database, 220 quasars are 
  detected in the VISTA VSA database with 130 objects in common with both
  WFCAM and VISTA data.  We give the necessary SQL queries syntax in Appendix~\ref{sec:SQL}.

@@

We use data from the the beginning of the WISE mission \citep[2010 January; ][]{Wright2010} through the fourth-year of NEOWISE-R operations \citep[2017 December;]{Mainzer2011}.  More specifically, we utilise the recently released ``unWISE Catalog'' \citet{MeisnerSchlafly2019}. The unWISE effort\footnote{http://unwise.me/} is the unblurred coadds of the WISE imaging using the AllWISE and NEOWISE-R stacked data \citep{Lang2014, Meisner2018a, Meisner2018b}. %{\bf Few more words here on the unWISE catalog...}.

All fluxes in the unWISE catalog are reported there are in ``Vega nanoMaggies'', with the Vega magnitude of a source is given by $m_{\rm Vega} = 22.5−2.5\log(f)$, where $f$ is the source flux. The absolute calibration for unWISE is ultimately inherited from AllWISE through the calibration of \citet{Meisner2017}. This inheritance depends on details of the PSF normalization at large radii, which is uncertain. Subtracting 4 mmag from the unWISE W1, and 32 mmag from unWISE W2 fluxes improves the agreement between unWISE and AllWISE fluxes.

Thus to convert unWISE Vega magnitudes onto the AB system, we have    
\begin{eqnarray*}
        {\rm W1}_{\rm AB, unWISE}  & = &   22.5 - 2.5 \log(f_{\rm W1}) - 0.004 + 2.699 \\
        {\rm W2}_{\rm AB, unWISE}  &  = &  22.5 - 2.5 \log(f_{\rm W2}) - 0.032 + 3.339 
\end{eqnarray*}
%Henceforth, when talking about we will simply refer to ``W1'' and ``W2'' as shorthand for ${\rm W1}_{\rm AB, unWISE}$ and {\rm W2}_{\rm AB, unWISE}
those two numbers are how far our flux measurements differed on average from the AllWISE flux estimates at high Galactic latitudes.  These tweaks will move you closer to the AllWISE absolute calibration, which we haven't tried to improve upon.
%We note though that 
%Especially in W1, though, this correction is uncertain, because the average offset between AllWISE and unWISE depends on magnitude, and we don't really know
%- what the source of the trend is,
%- which of unWISE and AllWISE is correct, or
%- where the AllWISE tie to AB/Vega was done (though presumably it was done on the bright end?).

For the our MIR variability investigations, we do not use the unWISE coadds, but instead use 
the \href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE} catalogue and the \href{http://wise2.ipac.caltech.edu/docs/release/neowise/neowise_2018_release_intro.html}{NEOWISE 2018 Data Release}. NEOWISE 2018 makes available the 3.4 and 4.6 μm (W1 and W2) single-exposure images and extracted source information that was acquired between 2016 December 13 and 2017 December 13 UTC, which was the fourth year of survey operations of the Near-Earth Object Wide-field Infrared Survey Explorer Reactivation Mission (NEOWISE; Mainzer et al. 2014, ApJ, 792, 30). The fourth year NEOWISE data products are concatenated with those from the first three years into a single archive.

@@

%\input{table_tex/THE_TABLE_v0pnt96_TOP10_betterformat}

\input{../tables_for_paper/output_table}

@@

\subsection{Colours}
Currently, very high-redshift quasars are identified by their morphology, flux and colours in optical and infrared imaging data \citet{Fan1999, Mortlock2012} Quasars are generally selected to be point sources, but  be outliers from the stellar locus in colour space. For VH$z$Qs, the main technique is to look for objects with extreme optical-to-near-infrared colours The lack of proper motion can also help identified quasars \citep[e.g.][]{Lang2009}.

\begin{figure*}
   \includegraphics[width=18.0cm]
   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_NIRcolors_20180704.pdf}
  \centering
   \caption[]
   {Infrared colour-spectral type and redshift plots for Late Type M/L/T dwarfs and the VH$z$Qs.
     {\it NB} I'm really not sure how Best et al. actually get their stellar sequence so clean. 
There are two types of spectral classification,  but restricting it to just SpT\_optn  or SpT\_nir removes
the blue or red end respectively. Hmmm....}
   \label{fig:SpecType_vs_NIRcolors}
 \end{figure*}

\begin{figure*}
   \includegraphics[width=18.0cm]
   {/cos_pc19a_npr/programs/quasars/highest_z/color_redshift/SpecType_vs_W1W2_W2W3colors_20180407.pdf}
  \centering
   \caption[]
   {Infrared colour-spectral type and redshift plots for Late Type M/L/T dwarfs and the VH$z$Qs.
}
   \label{fig:SpecType_vs_W1W2_W2W3colors}
 \end{figure*}

\subsection{L-$z$ Plane}
Having obtained an as-near-to-homogenous set of photometry as we can, 
we are now in a position to calculate the Absolute Magnitudes of the VH$z$Q 
sample and in particulare the absolute magnitude at rest-frame 1450\AA\ , $M_{1450}$, 
which is a key physical quantity and goes directly towards the quasar luminosity 
function and thus the reionization of hydrogen calculation.

We calculate the Distance Modulus in the normal fashion, 
\begin{equation}
m_{1450} - M_{1450} = 5 \log \left (    \frac{ D_{\rm L}(z)}{\rm Mpc}  \right )  + 25 + K_{\rm corr}(X,z)
\end{equation}
where $m_{1450}$ is the apparent magnitude at 1450\AA\ ,  
%$M_{1450}$ is the absolute magnitude at 1450 \AA\ , 
$D_{\rm L}(z)$ is the luminosity distance and 
$K_{\rm corr}(X,z)$ is the $K$-correction which corrects for the effects of redshifting of the bandpass and the spectrum.

The $m_{1450}$ apparent magnitude is derived from the $z-$, $y/Y-$ or $J-$band photometery.

The Pan-STARSS1 $z_{\rm PS1}$ and $y_{\rm PS1}$-bands approximatley
sample the redshift ranges $4.53\leq z \leq 5.45$ and $5.28\leq z \leq 6.47$, respectively 
for 1450\AA'\ emission, while the VIRCAM $Y_{\rm VIRCAM}-$ and $J_{\rm VIRCAM}$-bands 
cover $5.50\leq z \leq 6.57$ and $7.06\leq z \leq 8.16$.

\citet{Ross2013} has a detailed discussion of the $K$-correction (see that papers' Appendix B). 
The key result in that paper is, if quasars are described as having a power-law slope, 
$\alpha^{\nu}$ in spectral flux density, i.e., $f_\nu(\nu) \propto \nu^{\alpha_{\nu}}$ (as is conventional) 
then 
\begin{equation}
K_{\rm corr}(z) = -2.5 (1 + \alpha_{\nu}) \log[1 + z].
\end{equation}
Here the $[-2.5 \log(1 + z)]$ term corrects for the effective narrowing of the filter width with redshift, (the ``bandpass correction'') and the $[-2.5 \alpha^{\nu} \log(1 + z)]$ term takes into account the spectral index correction. The bandpass correction is approximately $\approx -1.945$ at redshift $z=5$ decreasing to $-2.32$ at redshift $z=7.50$.

%At $z=5.00$, the rest-frame 1450\AA\ emission is redshifted to 8700\AA\ observed, i.e., in the $z$-band, while at $z=6.00$, $z=5.00$

\begin{figure*}
  \includegraphics[width=18.0cm]
  {/cos_pc19a_npr/programs/quasars/highest_z/Lz/VHzQ_Lz_20180702.pdf}
  \centering
  \caption[]
  {The spectral bands used by different survey telescopes and that are relevant here.}
  \label{fig:Lz}
\end{figure*}

>>>>

This paper is organized as follows. In Section 2, we present the
assembled list of the 463 $z\geq5.00$ VH$z$Qs that we have
compiled. We then give a high-level overview of the photometric
surveys and datasets we use and present the photometry of the
VH$z$Qs. In Section 3 we investigate the variability properties of the
VH$z$Qs, looking for evidence of super-critical accretion. In Section
4 we calculate how many $z>5$ quasars we should expect to find in
current datasets. We conclude in Section 5 and present all the
necessary details to obtain our dataset in the Appendices.

We present all our photometry and magnitudes on the AB zero-point
system \citep{Oke_Gunn1983, Fukugita1996}.  This includes the
near-infrared, as well as the mid-infrared magnitudes. These
magnitudes are {\it not} Galactic extinction corrected.
%Appendix~\ref{sec:filters} gives the AB to Vega transforms for a wide range of optical, NIR and MIR filters. 
We use a flat $\Lambda$CDM cosmology with $H_{\rm 0} = 67.7$ km s$-1$ Mpc$−1$, $\Omega_{\rm
M} = 0.307$, and $\Omega_{\Lambda} = 0.693$ (Planck Collaboration et
al. 2016) to be consistent with \citet{Banados2016} and all logarithms
are to the base 10.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%    S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%    S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%    S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
%%trim=l b r t
%  \includegraphics[width=18.6cm, clip,trim=14mm 4mm 10mm 10mm]
  \includegraphics[width=8.6cm, clip,trim=32mm 4mm 32mm 10mm]
  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/filters_vs_QSOstars_z6pnt7.pdf}
  \centering
  \vspace{-12pt}
  \caption[]
  {The spectral bands used by different survey telescopes and that are relevant here.
    The $grizy$ filters are from the Pan-STARRS survey. The $JHK$ are from 
    UKIRT/WFCAM, while $K_{s}$ is a VISTA/VIRCAM filter. The 
    The narrow W-band centered at $\lambda\approx14,500$\AA\ is a CFHT/Wircam filter. 
    The WISE passbands  W1-4 are also presented.
    The quasar spectrum is a composite based on \citet{VdB2001} and 
    \citet{Banados2016}. The L and T dwarf spectra are from \citet{Cushing2006}. 
  }
  \label{fig:filters}
\end{figure}

@@

We have compiled a list of 463 quasars with redshifts $z\geq5.00$. We
use all the $z\geq5.00$ quasars that have been discovered,
spectroscopically confirmed and published as of 2018 December 31 (MJD
58483). We then obtain optical, near-infrared and mid-infrared
photometry for the spectral dataset. 
%The optical data comes from the Panoramic Survey Telescope and Rapid Response System (Pan-STARRS) survey \citep{Chambers2016}. 
The near-infrared data comes from two
sources: first, the WFCAM \citep[][]{Casali2007} on the UKIRT,
primarly, but not exclusively, as part of the UKIRT Infrared Deep Sky
Survey \citep[UKIDSS; ][]{Lawrence2007}.  And second, data from the
VIRCAM on the VISTA \citep[][]{Emerson2006, Dalton2006}. The
mid-infrared, $\lambda=3-30\mu$m wavelength data is from the the
Wide-Field Infrared Survey Explorer \citep[WISE;][]{Wright2010,
Cutri2013} mission. For reference, Figure~\ref{fig:filters} displays
the wavelength and normalised transmission of the filters in question.

\subsection{Spectroscopy} 
We compile the list of all known, spectroscopically confirmed
quasars from the literature.  This list was complied from a range of
surveys and papers.  Specifically, we use data from:
\citet{Banados2014, Banados2016, Banados2018}, 
\citet{Becker2015}, 
\citet{Calura2014}, 
\citet{Carilli2007, Carilli2010}, 
\citet{Carnall2015}, 
\citet{Cool2006}, 
\citet{DeRosa2011}, 
\citet{Fan2000, Fan2001c, Fan2003, Fan2004, Fan2006, Fan2018}, 
\citet{Goto2006}, 
\citet{Ikeda2017}, 
\citet{Jiang2008, Jiang2009, Jiang2015, Jiang2016},   
\citet{Kashikawa2015}, 
\citet{Koptelova2017}, 
\citet{Kim2015, Kim2018},  
\citet{Kurk2007, Kurk2009}, 
\citet{Leipski2014}, 
\citet{Mahabal2005}, 
\citet{Matsuoka2016,  Matsuoka2018a, Matsuoka2018b},   
\citet{Mazzucchelli2017}, 
\citet{Morganson2012}, 
\citet{Mortlock2009, Mortlock2011},
\citet{McGreer2006, McGreer2013},  
\citet{Reed2015, Reed2017}, 
\citet{Stern2007},  
\citet{Tang2017}, 
\citet{Venemans2007, Venemans2012, Venemans2013, Venemans2015a, Venemans2015b, Venemans2016},
\citet{WangF2016, WangF2017, WangF2018a, WangF2018b},
\citet{Willott2007, Willott2009, Willott2010a, Willott2013b, Willott2015}, 
\citet{Wu2015} 
\citet{YangJ2018a, YangJ2018b}  
and 
\citet{Zeimann2011}.

@@

  We detect 359 unique quasars in the WFCAM WSA database, 220 quasars are 
  detected in the VISTA VSA database with 130 objects in common with both
  WFCAM and VISTA data.  
  We give the necessary SQL queries syntax at 
  \href{https://github.com/d80b2t/VHzQ/blob/master/data/WSA_VSA/SAMPLE_SQL_QUERIES}{\tt d80b2t/VHzQ}.

@@

We use data from the the beginning of the WISE mission \citep[2010
January; ][]{Wright2010} through the fourth-year of NEOWISE-R
operations \citep[2017 December;]{Mainzer2011}.  More specifically, we
utilise the recently released ``unWISE Catalog''
\citet{Schlafly2019}. The unWISE effort\footnote{http://unwise.me/} is
the unblurred coadds of the WISE imaging using the AllWISE and
NEOWISE-R stacked data \citep{Lang2014, Meisner2018a, Meisner2018b}.

All fluxes in the unWISE catalog are reported there are in ``Vega
nanoMaggies'', with the Vega magnitude of a source is given by 
\begin{equation}
m_{\rm Vega} = 22.5 - 2.5\log(f),
\end{equation} 
where $f$ is the source flux. The absolute calibration for unWISE is
ultimately inherited from AllWISE through the calibration of
\citet{Meisner2017a}. This inheritance depends on details of the PSF
normalization at large radii, which is uncertain. Subtracting 4
millimag from the unWISE W1, and 32 millimag from unWISE W2 fluxes
improves the agreement between unWISE and AllWISE fluxes.

Thus to convert unWISE Vega magnitudes onto the AB system, we have:     
\begin{eqnarray*}
        {\rm W1}_{\rm AB, unWISE}  & = &   22.5 - 2.5 \log(f_{\rm W1}) - 0.004 + 2.699 \\
        {\rm W2}_{\rm AB, unWISE}  &  = &  22.5 - 2.5 \log(f_{\rm W2}) - 0.032 + 3.339. 
\end{eqnarray*}
For the our MIR variability investigations, we do not use the unWISE
coadds, but instead use the
\href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE}
catalogue and the
\href{http://wise2.ipac.caltech.edu/docs/release/neowise/neowise_2018_release_intro.html}{NEOWISE
2018 Data Release}. NEOWISE 2018 makes available the 3.4 and 4.6 μm
(W1 and W2) single-exposure images and extracted source information
that was acquired between 2016 December 13 and 2017 December 13 UTC,
which was the fourth year of survey operations of the Near-Earth
Object Wide-field Infrared Survey Explorer Reactivation Mission
(NEOWISE; Mainzer et al. 2014, ApJ, 792, 30). The fourth year NEOWISE
data products are concatenated with those from the first three years
into a single archive.

@@

%\input{table_tex/THE_TABLE_v0pnt96_TOP10_betterformat}
%\footnotesize
%\tiny
\begin{landscape}
      \input{../tables_for_paper/output_table}
\end{landscape}
%\normalsize

@@

At least 8 original observations across at least 30 days in either WSA or VSA per band, calibrated flux greater than zero over the whole time, and the error on the average flux is 8 times lower than this.

Thenn a requirement of SNR$>3$ per `average' epoch, where `average epoch' is then dependenet o nthe averaging timescales (whcih as we see can vary).

Then calculate the clipped median and standard deviation, 
\begin{equation}
1.48 \times \sigma_{median} / \bar{\epsilon}
\end{equation}
where $\bar{\epsilon}$ is the mean of the error in each point in the light curve, divided by the total number of points. 
%%
With this definition, although some of the objects have very well sampled, 
`average' light curves where you are averaging over e.g. a month, or two weeks.

Longer time-series, better SNR and moreover, $(1+z)$. 
Just selecting things that would
%%
Doing this independtly in each band...
%Variation

%% 
%% Object numbers: 54 VSA   MMTJ0215-0529,
%% objID: 162 is both VSA and WSA and  SDSSJ0959+0227
%%
objiD 164 is SDSSJ1000+0234, faint; very faint. 
SHELLQsJ0220-0432: (qso59) show this too. 
CFHQSJ0216-0455

\begin{figure}[H]
  \begin{subfigure}{}
    \centering
    \includegraphics[width=8.5cm]{../light_curves/MMTJ0215-0529LC_20190214.png}
    \caption{MMTJ0215-0529}
    \label{fig:MMTJ0215-0529}
  \end{subfigure}%
  \begin{subfigure}{}
    \centering
    \includegraphics[width=8.5cm]{../light_curves/CFHQSJ0216-0455LC_20190214.png}
    \caption{CFHQSJ0216-0455}
    \label{fig:CFHQSJ0216-0455}
  \end{subfigure}
  \begin{subfigure}{}\quad
    \centering
    \includegraphics[width=8.5cm]{../light_curves/SHELLQsJ0220-0432LC_20190214.png}
    \caption{SHELLQsJ0220-0432}
    \label{fig:SHELLQsJ0220-0432}
  \end{subfigure}
  \medskip
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 
%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
%%     S E C T I O N    4         S E C T I O N    4           S E C T I O N    4       S E C T I O N   4
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Surface Density of VH$z$Qs}
One interesting question to ask is given the compilation of VH$z$Qs assembled here, 
are there bright $z>5.00$ quasars that are in {\it current} photometric datasets, and if 
so, how many are still to be discovered and confirmed spectroscopcially?

VHS, Area 1: 150$<$RA/deg$<200$ annd $-40<$Decl./deg$<-20$:
$Y$=21.1 mag, $J$=20.6 mag, $H$=20.3 mag, $K_{s}$=19.8 mag (all AB). 
Area 2: 10$<$RA/deg$<$60, $-60<$Dec$<-40$:
$J$=21.2 mag, $H$=20.6 mag, $K_{s}$=20.2 mag.

VIKING is more uniform, so I calculated the averages over the whole area:
$Z$=22.7 mag, $Y$=21.9 mag, $J$=21.4 mag, $H$=21.2 mag, $Ks$=21.1 mag.

\begin{figure}[h]
  \centering
  \includegraphics[width=8.5cm]{../data/WSA_VSA/VHS_H_abMagLim.png}
  \caption{The calculated average {\tt AB MAGLIM} in the VHS.
    As one can see, VHS is not completely uniform. The are 3 areas with different filter sets, 
    and the depths changed in 2 of these areas, particularly in $J$ and $K_{s}$. 
    Y and H are almost uniform, but the coverage is much less.}
  \label{fig:1}
\end{figure}

Following \citet{Fan2001b} and \citet{McGreer2013}, we use use an
exponential decline to describe the space density of VH$z$Qs at high
redshifts, e.g.
\begin{equation}
\rho(z, {\rm M}_{1450} \propto 10^{k (z)}
\end{equation}
where $z$ is the sample redshift. 
%Fan, X., Strauss, M. A., Schneider, D. P., et al. 2001b, AJ, 121, 54

UHS J-band depth 19.6 \citep[Vega; ][]{Dye2018}

VISTA HEMISPHERE SURVEY DATA RELEASE 1
Release date (will be set by ESO)
PROPOSAL ESO No.: 179.A-2010
PRINCIPAL INVESTIGATOR: Richard McMahon
Authors: R. McMahon, M. Banerji, N. Lodieu for the VHS Collaboration

The aim of the Vista Hemisphere Survey (VHS) is to carry out a near
Infra-Red survey, which when combined with other VISTA Public Surveys
will result in coverage of the whole southern celestial hemisphere
($\sim$20,000 deg$^2$) to a depth 30 times fainter than 2MASS/DENIS in
at least two wavebands (J and K$_s$), with an exposure time of 60 seconds
per waveband to produce median 5σ point source (Vega) limits of $J =
20.2$ and $K_{S} = 18.1$. In the South Galactic Cap, $\sim$5000 deg$^{2}$ will be
imaged deeper with an exposure time of 120 seconds and also including
the H band producing median 5$\sigma$ point limits of: J = 20.6; H = 19.8; K$_{s}$ = 18.5. 
In this 5000 deg$^{2}$ region of sky deep multi-band optical (grizY)
imaging data will be provided by the Dark Energy Survey (DES). The
remainder of the high galactic latitude ($|b|>$30$^{\circ}$) sky will be imaged
in YJHK for 60sec per band to be combined with ugriz waveband
observations from the VST ATLAS survey. \\

VHS                   YJHK            99.99, 21.2,  21.2,  20.6,  20.0                (9) \\

{\tt ABmagLimits} for each survey in the database. \\
